Injrury Outcomes - WHW matrices

### 2020-07-31 summary_tables_outcomes.Rmd
Capitalize title

    cat('###', city, '\n')

@@

    index <- index + 1
    cat('\n')
    cat('####', cm, '\n')
    #print(kable(format(temp1, scientific = F), caption = paste('Who Hit Whom (WHW) for ', scen_names[i], 'scenario and ', cas_mode[j], ' mode')))

>>>>

    cat('###', stringr::str_to_title(stringr::str_replace(city, '_', ' ')), '\n')

@@

    index <- index + 1
    cat('\n')
    cat('#### Casualty mode: ', stringr::str_to_title(cm), '\n')
    #print(kable(format(temp1, scientific = F), caption = paste('Who Hit Whom (WHW) for ', scen_names[i], 'scenario and ', cas_mode[j], ' mode')))
